Can Auxiliary Indicators Improve COVID-19 Forecasting and Hotspot Prediction?

### 2021-06-19 forecast/paper/supplement-text.tex
Edit bootstrap supplement

As explained in Section 2.B. of the main paper, a (somewhat cynical)
hypothesis for why we see benefits in forecasting and hotspot
prediction is that the indicators are not actually providing useful
information but they are instead simply acting as a sort of ``implicit
regularization,''  leading to shrinkage on the autoregressive
coefficients, leading to less volatile predictions.  To investigate
this hypothesis, we consider fitting  ``noise features'' that in truth
should have zero coefficients.  Recall (from the main paper) that at each forecast date, we
train a model on 6,426 location-time pairs.  Indicator models are
based on six features, corresponding to the three autoregressive terms
and the three lagged indicator values.  To form noise features
we resample from other rows.  In particular, at each location $\ell$ and
time $t$, we replace the triplet $(X_{\ell,t}, X_{\ell,t-7},
X_{\ell,t-14})$ by the triplet $(X_{\ell^*,t^*}, X_{\ell^*,t^*-7},
X_{\ell^*,t^*-14})$, where $(\ell^*,t^*)$ is a location-time pair
sampled with replacement from the 6,426 location-time pairs.  Figures
\ref{fig:fcast-booted}--\ref{fig:hot-booted} show the results.  No
method exhibits a noticeable performance gain over the \ar~method,
leading us to dismiss the implicit regularization hypothesis.

\attn{Would be good for someone to double check that the bootstrap
  procedure is correctly described.}

>>>>

As explained in Section 2.B. of the main paper, a (somewhat cynical)
hypothesis for why we see benefits in forecasting and hotspot
prediction is that the indicators are not actually providing useful
information but they are instead simply acting as a sort of ``implicit
regularization,''  leading to shrinkage on the autoregressive
coefficients, leading to less volatile predictions.  To investigate
this hypothesis, we consider fitting  ``noise features'' that in truth
should have zero coefficients.  Recall (from the main paper) that at each forecast date, we
train a model on 6,426 location-time pairs.  Indicator models are
based on six features, corresponding to the three autoregressive terms
and the three lagged indicator values.  To form noise indicator features,
we resample from other rows (while keeping the autoregressive
features fixed).  In particular, at each location $\ell$ and
time $t$, for the forecasting task we replace the triplet $(X_{\ell,t}, X_{\ell,t-7},
X_{\ell,t-14})$ in Eq. (3) of the main paper with the triplet $(X_{\ell^*,t^*}, X_{\ell^*,t^*-7},
X_{\ell^*,t^*-14})$, where $(\ell^*,t^*)$ is a location-time pair
sampled with replacement from the 6,426 location-time pairs.  
Likewise in the hotspot prediction task, we replace the triplet $(X_{\ell,t}^\Delta, X_{\ell,t-7}^\Delta,
X_{\ell,t-14}^\Delta)$ in Eq. (5) of the main paper with $(X_{\ell^*,t^*}^\Delta, X_{\ell^*,t^*-7}^\Delta,
X_{\ell^*,t^*-14}^\Delta)$.
Figures
\ref{fig:fcast-booted}--\ref{fig:hot-booted} show the results.  No
method exhibits a noticeable performance gain over the \ar~method,
leading us to dismiss the implicit regularization hypothesis.
